Probabilistic Forecasting of Geomagnetic Indices using Gaussian Process Models

### 2017-04-19 chap.tex
Added subsections to final section

\section{One Hour Ahead $Dst$: Formulation} \label{sec:osa}

@@

\section{One Hour Ahead $Dst$: Model Design}\label{sec:modeldesign}

@@

\section{GP-AR and GP-ARX: Workflow Summary}

@@

@@

Figures \ref{fig:CompareMaeARX} and \ref{fig:CompareCCARX} break down the results for GP-ARX by the model selection routine used. Apart from the general trend observed in \ref{fig:CompareMae} and \ref{fig:CompareCC}, we also observe that \emph{grid search} and \emph{coupled simulated annealing} give superior performance as compared to gradient based \emph{maximum likelihood}.

From the validation results, we can chose the model order which yields the best performance, for GP-AR it is $p_t = 6$ while for GP-ARX it is $p_t = 11$. Further examination of the validation results shows that in the scheme $p_t = 11$ choosing $p = 7, p_v = 1, p_b = 3$ gives superior results.

@@

@@

>>>>

\section{One Hour Ahead $Dst$ Prediction: Formulation} \label{sec:osa}

@@

\section{One Hour Ahead $Dst$ Prediction: Model Design}\label{sec:modeldesign}

@@

\section{GP-AR and GP-ARX: Workflow Summary}\label{sec:workflow}

@@

After running the workflow steps as outlined in section \ref{sec:workflow} above, we can understand the performance of the GP-AR and GP-ARX family of models on task of $Dst$ prediction in the following charts.

\subsection*{Model Selection \& Validation Performance}

@@

From the validation results, we can choose the model order which yields the best performance, for GP-AR it is $p_t = 6$ while for GP-ARX it is $p_t = 11$. Further examination of the validation results shows that in the scheme $p_t = 11$ choosing $p = 7, p_v = 1, p_b = 3$ gives superior results.

\subsection*{Comparison of Hyper-parameter Selection Algorithms}
Figures \ref{fig:CompareMaeARX} and \ref{fig:CompareCCARX} break down the results for GP-ARX by the model selection routine used. Apart from the general trend observed in \ref{fig:CompareMae} and \ref{fig:CompareCC}, we also observe that \emph{grid search} and \emph{coupled simulated annealing} give superior performance as compared to gradient based \emph{maximum likelihood}.

@@

\subsection*{Final Evaluation}

@@

\subsection*{Sample Predictions with Error Bars}
